GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator

### 2022-08-29 src/tex/ms.tex
[showyourwork] overleaf sync

% \input{captions/fig1.tex}

\begin{figure*}[htb!]
\gridline{\fig{figures/fig1a.pdf}{0.4\textwidth}{}}
          % \fig{figures/fig1b.pdf}{0.55\textwidth}{}}
\caption{Temporal and spatial variability in input bisectors encode turbulent granulation velocities. \textbf{Left:} To capture the line-of-sight variation observed in solar bisectors, observations were carried out at many discrete disk positions along each of the four solar limbs plus disk center. Figure adapted from Figure 1 of \citetalias{Lohner-Bottcher2018}. \textbf{Right:} Line bisectors differ in shape with both time and apparent position on the solar disk. From disk center ($\mu = 1$) to the limb ($\mu = 0$), bisectors transition from a distorted ``C"-shape to something more resembling a ``\textbackslash"-shape. This behavior results from the different viewing angles of convective granules along different lines of sight \citep[Figure 17.13 of ][]{Gray2008}. The solid, \revise{dashed, and dotted} lines trace the time-averaged bisector for each limb position. The shaded regions correspond to the $\pm1\sigma$ temporal variability of the bisectors at each limb position. Error bars in velocity are not shown; with an absolute wavelength calibration accuracy on order $\sim$$0.02$ m\AA\ ($\sim$1 $\ms$), the observed temporal variations are much larger than the typical uncertainty. \label{fig:one}}
\end{figure*}

>>>>

% \input{captions/fig1.tex}
\begin{figure*}[htb!]
\gridline{\fig{figures/fig1a.pdf}{0.4\textwidth}{}
          \fig{fig1b.pdf}{0.55\textwidth}{}}
\caption{Temporal and spatial variability in input bisectors encode turbulent granulation velocities. \textbf{Left:} To capture the line-of-sight variation observed in solar bisectors, observations were carried out at many discrete disk positions along each of the four solar limbs plus disk center. Figure adapted from Figure 1 of \citetalias{Lohner-Bottcher2018}. \textbf{Right:} Line bisectors differ in shape with both time and apparent position on the solar disk. From disk center ($\mu = 1$) to the limb ($\mu = 0$), bisectors transition from a distorted ``C"-shape to something more resembling a ``\textbackslash"-shape. This behavior results from the different viewing angles of convective granules along different lines of sight \citep[Figure 17.13 of ][]{Gray2008}. The solid, \revise{dashed, and dotted} lines trace the time-averaged bisector for each limb position. The shaded regions correspond to the $\pm1\sigma$ temporal variability of the bisectors at each limb position. Error bars in velocity are not shown; with an absolute wavelength calibration accuracy on order $\sim$$0.02$ m\AA\ ($\sim$1 $\ms$), the observed temporal variations are much larger than the typical uncertainty.}
\label{fig:one}
\script{fig1b.py}
\end{figure*}
